The Place of the Local Group in the Cosmic Web

### 2014-07-28 paper/main.tex
paper updated with the latest plots

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_nall_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_nall_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_nall_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal vector
$\hat{n}$, and the eigenvectors defining the cosmic web.
    \label{fig:alignment}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_rall_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_rall_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_rall_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the unit
  vector linking the two halos, $\hat{r}$, and the eigenvectors
  defining the cosmic web.
    \label{fig:alignment_r}}  
\end{figure}

@@

%% \begin{figure}
%% \begin{center}
%%   \includegraphics[width=0.48\textwidth]{scheme.pdf} 
%% \caption{Schematic picture of the strongest alignment tendencies in
%%   the the General and $2\sigma$-$3\sigma$ samples. The alignment
%%   between the peculiar velocities and the $\hat{e}_3$ eigenvector was
%%   reported in \citet{ForeroRomero2014} for all halos regardles of its
%%   mass. The flip in the alignment in the vector connecting the two
%%   dominant halos in pairs is a summary of the results in Figure
%%   \ref{fig:alignment}. 
%% \label{fig:scheme}}
%% \end{center}
%% \end{figure}

%\begin{figure*}
%\begin{center}
%  \includegraphics[width=0.49\textwidth]{ELL_histogram_filament.pdf}
%  \includegraphics[width=0.49\textwidth]{PROL_histogram_filament.pdf}
%  \includegraphics[width=0.49\textwidth]{ELL_histogram_sheet.pdf}
%  \includegraphics[width=0.49\textwidth]{PROL_histogram_sheet.pdf}
%\end{center}
%\caption{Cumulative distributions for the ellipticity and prolateness.
%    \label{fig:ELL_PROL}}  
%\end{figure*}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_n_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_n_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_n_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal vector
$\hat{n}$, and the eigenvectors defining the cosmic web.
    \label{fig:alignment}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the unit
  vector linking the two halos, $\hat{r}$, and the eigenvectors
  defining the cosmic web.
    \label{fig:alignment_r}}  
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{scheme.pdf} 
    \caption{Schematic picture of the strongest alignment tendencies in
      the the General and $2\sigma$-$3\sigma$ samples. The alignment
      between the peculiar velocities and the $\hat{e}_3$ eigenvector was
      reported in \citet{ForeroRomero2014} for all halos regardles of its
      mass. 
      \ref{fig:alignment}. 
      \label{fig:scheme}}
  \end{center}
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{alignments_jj_all_environments.pdf}
\end{center}
\caption{Alignment between the two angular momentum vectors of the two
  halos in the pair.
    \label{fig:jj_alignment}}  
\end{figure*}
